---
title: "Bumble bees, then and now: mapping change on Galiano Island"
date: 2026-07-04
draft: true
_build:
  render: never
  list: never
tags: ["community science", "bumble bees", "extirpation", "Galiano Island"]
summary: "A template research note — historical records, a community-mapped survey, and a look at what quietly shifts in a pollinator community over decades."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

*This is a template post demonstrating the range of content a research note on this
site can hold — a static figure, an interactive map, a collapsible methods section, and
a set of related links. The figure below uses illustrative placeholder data, not the
published results; swap in the real numbers when adapting this post.*

Historical museum specimens and present-day community science observations rarely speak
to each other directly — different collectors, different effort, different decades. But
laid side by side, they can reveal quiet shifts in a pollinator community that neither
record shows alone.

<div class="pageinfo">
<strong>Key idea</strong> — absence of a record is not evidence of absence. A species
can be locally extirpated for years before that absence is even noticed, let alone
confirmed.
</div>

```{r bee-detections, fig.cap="Illustrative comparison of historical museum records and contemporary community-mapped observations by species (placeholder data)."}
library(ggplot2)

set.seed(47)
species <- c("B. mixtus", "B. flavifrons", "B. sitkensis", "B. vosnesenskii", "B. californicus")
demo_data <- data.frame(
  species = rep(species, 2),
  period = rep(c("Historical (pre-2000)", "Contemporary (2016-2025)"), each = length(species)),
  detections = c(18, 22, 9, 4, 11, 6, 19, 0, 15, 3)
)
demo_data$period <- factor(demo_data$period, levels = c("Historical (pre-2000)", "Contemporary (2016-2025)"))

ggplot(demo_data, aes(x = species, y = detections, fill = period)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  scale_fill_manual(values = c("#8A8577", "#7FA83E")) +
  labs(x = NULL, y = "Detections", fill = NULL) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "top", panel.grid.minor = element_blank())
```

Two patterns worth a second look: *B. californicus* drops from a modest historical
presence to zero contemporary detections despite substantial community search effort —
a candidate for local extirpation. *B. vosnesenskii*, rarely recorded historically, now
turns up regularly — a possible range shift or simply better detection through
iNaturalist-literate observers.

Community-mapped survey effort itself is worth showing, not just summarizing — search
effort is part of the evidence, not just a caveat.

```{r survey-map}
library(leaflet)

sites <- data.frame(
  name = c("Bellhouse Park", "Montague Harbour", "Dionisio Point", "Bodega Ridge"),
  lat  = c(48.9214, 48.8944, 48.9985, 48.8767),
  lng  = c(-123.3487, -123.3961, -123.3735, -123.4653)
)

leaflet(sites) |>
  addTiles() |>
  setView(-123.42, 48.92, zoom = 12) |>
  addCircleMarkers(~lng, ~lat, label = ~name, radius = 8,
                    color = "#b6491f", fillOpacity = 0.85, stroke = FALSE)
```

<details class="research-details">
<summary>Survey methodology (placeholder — replace with real methods)</summary>
<p>Historical records compiled from museum specimen databases (e.g. GBIF-mediated
collections). Contemporary records drawn from community-mapped iNaturalist
observations, 2016–2025, restricted to research-grade identifications. Search effort
estimated from GPS track density, following the same approach used in the
<a href="https://github.com/IMERSS/detecting-local-extinction">extirpation detection protocol</a>.</p>
</details>

This kind of comparison is really a small-scale version of the same question at the
heart of
[Simon, Best & Starzomski (2023)](https://doi.org/10.3955/046.096.0305) — what
does it take to responsibly claim a species has disappeared from a place, rather than
simply gone unnoticed? It is also, not coincidentally, the same question the diatom
monitoring work and the broader extirpation framework keep returning to at different
scales.

### Related

<div class="related-links">
<a href="http://biogaliano.org"><strong>Biodiversity Galiano</strong><span>Community-based biodiversity monitoring on Galiano Island</span></a>
<a href="https://imerss.org"><strong>IMERSS</strong><span>Institute for Multidisciplinary Ecological Research in the Salish Sea</span></a>
<a href="https://github.com/IMERSS/detecting-local-extinction"><strong>Detecting extirpation</strong><span>Protocol and documentation for the extirpation detection method</span></a>
</div>
